### 2014-09-10 paper/paper.Rmd
small tweaks - but think the countries are messed up for the gender plots

# 1. The gender gap in math is not universal but the reading gap is, in favor of girls

@@

@@

# 3. Starting school at an older age generated lower average math score.

@@

# 4. Time spent out of school studying is important, but only up to a point

@@

# 5. Parents matter
### a. Number of parents in the home
Looking at the number of parents in a household shows that student in two-parent household are on average performing better than student's not in a two-parent household. Students with just a mother at home do tend to perform better than students with only a father at home. Students with no parents at home are performing the worst, on average.

@@

# 7. More TVs yield higher math scores in the developing world, but lower in the developed countries

@@

### Play with the data yourself

>>>>

# 1. The gender gap in math is not universal but the reading gap is, in favor of girls.

@@

*** Looks like I messed up the colors for countries - need to check this again

@@

# 3. Starting school at an older age generates lower average math scores.

@@

# 4. Time spent out of school studying is important, but only up to a point.

@@

# 5. Parents matter!
### a. Number of parents in the home
Looking at the number of parents in a household shows that student in two-parent household are on average performing better than student's not in a two-parent household. Students with just a mother at home do tend to perform better than students with only a father at home. Students with no parents at home are performing the worst, on average.

@@

# 7. More TVs yield higher math scores in the developing world, but lower in the developed countries.

@@

### Play with the data yourself.
